% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{paralist}

\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}


% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

\newcommand{\xhdr}[1]{\vspace{3pt}\noindent\textbf{#1}}
%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{AI539}
\def\confYear{W2023}


\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{AI Interview Coach: Optimizing Software Engineering Interview Feedback through RLAIF and DPO}

\author{Chun-Han Chien \hspace{15pt} Yun-Chen Huang \hspace{15pt} Masaki Kitagawa \hspace{15pt} Deng-Chyi Yang\\
Oregon State University\\
{\tt\small \{chiench, huangyun, kitagawm, yangden\}@oregonstate.edu}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   Preparing for software engineering interviews is a critical but resource-intensive process for computer science students. While large language models (LLMs) offer a scalable solution for automated coaching, their feedback often lacks the specificity and actionability required for high-stakes technical interviews. In this project, we build an AI Interview Coach based on Qwen2.5-3B-Instruct and attempt to improve it through Reinforcement Learning from AI Feedback (RLAIF) and Direct Preference Optimization (DPO), using a stronger judge model (Qwen3.5-9B) to generate preference data over a five-dimension coaching rubric. On a fixed 200-example test set, the SFT+DPO model attains a marginally higher mean judge score than the baseline (17.03 vs.\ 16.86 on a 1--20 scale), but the difference is not statistically significant (paired $t$-test $p=0.42$; Wilcoxon $p=0.70$; Cohen's $d=0.057$). A per-item failure analysis shows that genuine gains---notably the removal of baseline hallucinations---are offset by newly introduced technical errors, and that a strong ceiling effect (65\% of baseline outputs already score $\geq 18/20$) together with a coarse, homogeneous evaluation set limits the measurable benefit. We discuss the methodological implications for evaluating preference optimization with LLM judges.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

The technical interview is a gatekeeping milestone in the software engineering industry. Success requires not only strong algorithmic knowledge but also the ability to communicate complex technical concepts clearly and efficiently. However, many students, particularly at the graduate level, lack access to personalized, high-quality coaching that can identify subtle gaps in their technical explanations or communication styles.

Traditional automated systems often provide generic feedback that fails to address the specific nuances of a student's answer. Large language models (LLMs) show promise in this domain, yet base models often struggle to maintain a consistent coaching persona that is both technically rigorous and pedagogically supportive. 

This work aims to bridge this gap by fine-tuning a lightweight, efficient LLM (Qwen2.5-3B) to act as a specialized interview coach. By leveraging a more powerful judge model (Qwen3.5-9B) to provide feedback on feedback (RLAIF), we create a robust dataset of preferences that prioritize technical precision and actionable advice. We use Direct Preference Optimization (DPO) with QLoRA to refine the model's behavior, ensuring it provides feedback that is specifically tailored to the requirements of software engineering interviews.

\section{Related Work}
\label{sec:related}

\xhdr{RLHF and RLAIF.} Reinforcement Learning from Human Feedback (RLHF) has been the standard for aligning LLMs with human values \cite{ouyang2022instructgpt}. However, gathering human preferences is slow and expensive. Reinforcement Learning from AI Feedback (RLAIF) has emerged as a viable alternative, where a stronger "teacher" model provides preferences to train a "student" model, often achieving performance comparable to human-labeled data \cite{bai2022constitutional}.

\xhdr{Direct Preference Optimization.} DPO simplifies the RLHF pipeline by optimizing the policy model directly from preference pairs without the need for a separate reward model \cite{rafailov2023dpo}. This makes it particularly suitable for constrained compute environments where training a complex reward model is impractical.

\xhdr{AI in Education.} Recent work has explored LLMs for automated grading and feedback in programming and STEM education. LLM-based feedback can draw on intelligent tutoring systems and learning sciences to improve pedagogical quality \cite{stamper2024enhancing}. Since our pipeline relies on an LLM judge, we also consider recent findings on aligning LLM-assisted evaluation with human preferences \cite{shankar2024validators}. However, most existing tools focus on code correctness rather than the conversational and descriptive technical communication required in interviews.

\section{Methodology}
\label{sec:method}

Our pipeline consists of four phases: (i) dataset construction and student-answer simulation, (ii) preference-candidate generation with bias control, (iii) preference labeling via an LLM judge (RLAIF), and (iv) model optimization with SFT and DPO. Throughout, the policy model that is fine-tuned is Qwen2.5-3B-Instruct, and a stronger Qwen3.5-9B model serves as the judge.

\subsection{Dataset and Student Simulation}
We build the dataset from two software engineering interview question sources (an internal \emph{Software Questions} set and a public \emph{ai\_interview\_questions} set). After preprocessing we obtain 4,653 training examples and a held-out test set of 200 examples. Each example pairs an interview question with a reference answer, category and difficulty metadata, and a simulated student answer.

To probe the coach under realistic conditions, we simulate answers from a fixed persona---a first-year CS Master's student with strong fundamentals but limited industry experience, prone to omitting edge cases and using imprecise terminology. Using this persona, we prompt the base model to produce five student-answer types spanning the common failure modes:
\begin{itemize}
    \item \textbf{Correct but incomplete:} missing edge cases or optimizations.
    \item \textbf{Partially correct:} a sound core with notable gaps or errors.
    \item \textbf{Incorrect:} a fundamentally wrong approach.
    \item \textbf{Too vague:} lacking technical depth or specific terminology.
    \item \textbf{Verbose but unfocused:} burying the answer in irrelevant detail.
\end{itemize}
Crucially, the simulated student answers and the test questions are generated \emph{once} and then frozen: the identical inputs are reused for baseline evaluation, preference generation, and final evaluation. This design isolates the coaching model as the only variable, so any score difference is attributable to fine-tuning rather than to changes in the inputs. We note, however, that in the released data used for the experiments in this paper every train and test item carries the single label \texttt{partially\_correct}, and category/difficulty metadata is \texttt{Unknown} for most items; the evaluation therefore exercises only this subset of the intended answer types (see \cref{sec:discussion}).

\subsection{Preference Candidate Generation}
For each training example, the base model generates two coaching feedback candidates (\texttt{feedback\_a}, \texttt{feedback\_b}) for the same fixed student answer. To prevent the preference data from encoding superficial cues, we draw each candidate from a randomized but reproducible feedback style, sampled from a pool of distinct coaching styles---\emph{technical precision focus}, \emph{interview communication focus}, \emph{balanced coaching} (strengths/weaknesses/advice), and \emph{supportive yet strict}---generated at varied temperatures. The A/B slot is not tied to a fixed quality level, and we log the style, temperature, and candidate model for each side. This reduces the risk that the downstream model learns spurious patterns such as preferring the second candidate, longer responses, or a particular style.

\subsection{Preference Labeling via RLAIF}
We employ Qwen3.5-9B as the judge. It scores feedback on five dimensions---Technical Correctness, Specificity, Helpfulness, Actionability, and Interview Coaching Quality---each on a 1--20 scale, with the top band (18--20) reserved for ``exceptional'' feedback containing concrete code or master-class guidance. For preference selection the judge compares the two candidates and is explicitly instructed to ignore A/B position, length, formatting, tone alone, and style label, basing its choice only on coaching quality. The selected candidate becomes the \textit{chosen} response and the other the \textit{rejected} response, yielding the preference pairs used for DPO.

\subsection{Model Optimization}
We fine-tune with QLoRA (Quantized Low-Rank Adaptation), training lightweight adapter weights rather than the full model to fit our compute budget. Optimization proceeds in two stages:
\begin{compactenum}
    \item \textbf{SFT (Supervised Fine-Tuning):} we first build a supervised dataset that maps the (question, reference answer, student answer) input to the judge-preferred \textit{chosen} feedback, and train on it to establish the general coaching format and persona.
    \item \textbf{DPO (Direct Preference Optimization):} starting from the SFT model, we train on the RLAIF-labeled \textit{chosen}/\textit{rejected} pairs to directly optimize for the coaching rubric without a separate reward model.
\end{compactenum}

\input{results_section}

\section{Conclusion}
\label{sec:conclusion}

We built an AI Interview Coach by fine-tuning Qwen2.5-3B with SFT and DPO on RLAIF-labeled preference data, and evaluated it against the baseline with an LLM judge on a fixed 200-example test set. The trained model scored marginally higher on every rubric dimension, but no difference was statistically significant, and the effect size was negligible. Our failure analysis explains why: the judge saturates near the top of its scale (a ceiling effect), its scores are low-resolution, the evaluation set is homogeneous (all test answers share a single answer-type label), and real improvements are cancelled by occasional new technical errors introduced during preference optimization. Rather than a clear win, our main contributions are negative but instructive: (i) LLM judges that saturate are weak instruments for detecting incremental alignment gains, motivating pairwise/win-rate evaluation and finer rubrics; (ii) reference-free DPO can introduce fluent but false technical claims, motivating a factuality-grounded preference signal. Future work includes rebuilding a diverse test set across all student-answer types and difficulties, a small-scale human evaluation to validate the judge, and grounding the coach against reference answers.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}
